### 2012-11-13 doc/progress_plan/report.tex
Finished web framework comparisons

Partridge is based upon several fairly complex and new ideas in AI and NLP.
For the project to be a success it is imperative that the right language,
environment and toolkits are used to avoid unnecessary work on existing
technologies and allow priority to be given to the novel aspects of the
project.

@@

\subsubsection{User Interface Style}

@@

>>>>

@@

@@

Partridge's web frontend will be used by researchers to wish to query the
system for information on scientific papers. As it is a web tool, Partridge
will be presented as a set of HTML web pages.

It is possible to use a separate software stack Such as Apache web server
(\url{http://httpd.apache.org/}) and PHP (\url{http://www.php.net}) as a web
presentation layer. However, this would involve adding more software to the
project and building an interface between the PHP scripts and Partridge's
python backend. To prevent unnecessary complication, this approach will be
avoided and instead, a Python web toolkit will be used and integrated directly
with the backend.

Django (\url{http://www.djangoproject.com/}) is a Python web framework with
integrated database management and templating capabilities \cite{django2012}.
The framework provides automatic management of all aspects of your
application's data storage systems unless explicitely disabled. The framework
also uses a fairly stricty Model-View-Controller pattern and this is enforced
in the structure of the application code. These features may be useful in a
general web application such as a news site. Partridge requires a much more
complex internal structure to take into account the machine learning and NLP
aspects of the system. Having to `shoehorn' Partridge into a specific structure
to make it compatible with Django adds extra overhead to the project and is not
desirable.

Flask (\url{http://flask.pocoo.org}) is a python `microframework' for web
development. Ronacher (2012) writes that ``Flask aims to keep the core simple
but extensible...[and] won't make any decisions for you\cite{flask2012}." It
uses a simple templating system that can optionally be swapped out for an
equivalent system and does not impose any limitations or requirements on the
layout of the program or the type of database that is used. Flask integrates
very simply into existing software using Python annotations\emph{(Ibid)}. This approach
means that the framework could be adapted to Partridge very quickly, rather
than requiring Partridge to be adapted to the framework. Therefore, Flask has
been chosen as the preferred web framework for use in the project.
